Cybersecurity Is Too Important\\To Be Left To The Specialists

### 2019-06-15 FIE2019-final-TPJHD.tex
JHD tidying

\begin{abstract}
% submitted abstract (100-500 word limit):
There are numerous facets to cybersecurity education, from theory to practice, hardware and software, to social and technical (as well as other important dimensions). A multitude of national and international model curricula and recommendations - from national academies, learned societies and even governments -- have been presented and discussed in recent years, with varying levels of impact on policy and practice. In this paper we attempt to address the key questions ``what should the generalist computer scientist/engineer know'' and ``how well is that being taught''. (Cyber)security -- if thought about at all -- has historically been left to specialists, frequently viewed as a masters-level discipline; or left for development in professional practice, sometimes called ``information assurance'' in the UK and Europe, which worked, even if not well, in a sequential process model.

@@

\subsection{CyberSecurity: for all or for specialists?}
In one sense, this title is a false dichotomy: there is a serious need for cybersecurity specialists (estimates vary, but are always large: \cite{JCNSS2018a} has only anecdotal evidence), but also all in IT need to know \emph{some} cybersecurity. In this section we illustrate this by briefly exploring four cases, General Data Protection Regulation (GDPR), Agile development, one industry sector (with rigorous demands for secure software) and impact of these cases upon one another.

@@

There has been substantial Computer Science /digital curriculum reform across the
UK~\cite{crick+sentance:2011,brown-et-al:sigcse2013,wgictreview:2013,brown-et-al:toce2014,moller+crick:jce2018}
--- but what has happened to the focus on cybersecurity?  The Institute of Coding \cite{Davenportetal2019a}, designed to improve digital skills for UK graduates, does indeed mention cybersecurity, but merely as a sub-item in one work package (1.2a).

UK national economic skills priority
e.g. \url{https://www.gov.uk/government/publications/national-cyber-security-strategy-2016-to-2021}
%(esp. \url{https://publications.parliament.uk/pa/jt201719/jtselect/jtnatsec/706/70605.htm}
(especially \cite{JCNSS2018a}
and \url{https://www.ncsc.gov.uk/blog/skills-and-training} and
\url{https://www.cybersecuritychallenge.org.uk/}).

@@

In the context of BCS accreditation, these requirements imply an exit standard that all students on a programme must be able to demonstrate irrespective of the option choices they have made. This means a HEI applying for accreditation is expected to provide evidence that the criteria are taught and assessed in a non-trivial manner, to and by all students upon the programme seeking accreditation . A HEI is expected to provide evidence in the form of programme and module specification documentation and example assessment specifications (coursework and examinations). These criteria and the expectation that they are taught and assessed has been present for a number of years.

>>>>

\begin{abstract}
% submitted abstract (100-500 word limit):
There are numerous facets to cybersecurity education, from theory to practice, hardware and software, to social and technical (as well as other important dimensions). A multitude of national and international model curricula and recommendations 
%-- from national academies, learned societies and even governments -- 
have been presented and discussed in recent years, with varying levels of impact on policy and practice. In this paper we attempt to address the key questions ``what should the generalist computer scientist/engineer know'' and ``how well is that being taught''. (Cyber)security -- if thought about at all -- has historically been left to specialists, frequently viewed as a masters-level discipline; or left for development in professional practice, sometimes called ``information assurance'' in the UK and Europe, which worked, even if not well, in a sequential process model.

@@

\subsection{CyberSecurity: for all or for specialists?}
In one sense, this title is a false dichotomy: there is a serious need for cybersecurity specialists (estimates vary, but are always large%: \cite{JCNSS2018a} has only anecdotal evidence   %JHD - do we need this, as its only anecdotal?
), but also all in IT need to know \emph{some} cybersecurity. In this section we illustrate this by briefly exploring four cases, General Data Protection Regulation (GDPR), Agile development, one industry sector (with rigorous demands for secure software) and impact of these cases upon one another.

@@

There has been substantial Computer Science /digital curriculum reform across the
UK~\cite{crick+sentance:2011,brown-et-al:sigcse2013,wgictreview:2013,brown-et-al:toce2014,moller+crick:jce2018}
--- but what has happened to the focus on cybersecurity?  The Institute of Coding \cite{Davenportetal2019a}, designed to improve digital skills for UK graduates, does indeed mention cybersecurity, but merely as a sub-item in one work package (1.2a). There is little connection with 
UK national economic skills priority,
e.g. \url{https://www.gov.uk/government/publications/national-cyber-security-strategy-2016-to-2021}
%(esp. \url{https://publications.parliament.uk/pa/jt201719/jtselect/jtnatsec/706/70605.htm}
(especially \cite{JCNSS2018a}
and \url{https://www.ncsc.gov.uk/blog/skills-and-training} and
\url{https://www.cybersecuritychallenge.org.uk/}).

@@

In the context of BCS accreditation, these requirements imply an exit standard that all students on a programme must be able to demonstrate irrespective of the option choices they have made. This means a HEI applying for accreditation is expected to provide evidence that the criteria are taught and assessed in a non-trivial manner, to and by all students upon the programme seeking accreditation. A HEI is expected to provide evidence in the form of programme and module specification documentation and example assessment specifications (coursework and examinations). These criteria and the expectation that they are taught and assessed has been present for a number of years.
